Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-01-20 ms.tex
compare aligned versus un-aligned dynamic spectrum.

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{o9LEDwFlat_dyn_spec_NRCN83-256-O9LW.pdf}{0.55\textwidth}{Dynamic Spectrum}
\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Broadband Time Series}}
%\gridline{\fig{o9LEDwFlat_ind_spec_NRCN83-256-O9LW.pdf}{0.44\textwidth}{Representative Spectrum}
%}
\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes), that also show up in the integrated broadband time series.
The effect of image motion along the dispersion direction is visible as broad stripes
}\label{fig:otisLWdynSpec}
\end{figure*}

@@

\subsection{Using SW centroid for LW grism}

>>>>

\begin{figure*}
%\gridline{\fig{tser_LW_OTIS.pdf}{0.99\textwidth}{WLP8 Image} }
\gridline{\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW}{0.49\textwidth}{Dynamic Spectrum}
\fig{o9LEDwf322w2Flat_dyn_spec_NRCN83-256-O9LW_aligned}{0.49\textwidth}{Dynamic Spectrum with Alignment}}
\caption{The dynamic spectrum of the grism along shows large artifacts due to motion of the source (broad horizontal stripes).
These are dramatically reduced when using cross correlation
}\label{fig:otisLWdynSpec}
\end{figure*}

%\begin{figure*}
%\fig{o9LEDwFlat_bb_series_NRCN83-256-O9LW.pdf}{0.41\textwidth}{Broadband Time Series}
%\end{figure*}

@@

\clearpage
\subsection{Using SW centroid for LW grism}
